Data Exploration: IUCN and AquaMaps

### 2016-03-22 data_explore/data_explore.Rmd
All figures done? slap 'em together in Photoshop now.

knitr::kable(taxa_df %>%
               dplyr::select(class, 
                             AquaMaps = n_am_class_all, 
                             IUCN = n_iucn_class_all, 
                             Both = n_class_both))
```

@@

bar_taxa2 <- ggplot(taxa_df_long2, aes(x = class, y = percent, fill = dataset)) +
  ggtheme_plot + 
  theme(panel.grid.major.x = element_blank()) +
  geom_bar(stat = 'identity', alpha = .8) +
#  scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
  scale_fill_manual(values = c('AquaMaps' = '#1b9e77', 'Both' = '#d95f02', 'IUCN' = '#7570b3')) +
  geom_text(aes(label = sprintf('n = %s', n_total), y = 102), 
            size = 2, 
            angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 130),
                     breaks = c(0, 25, 50, 75, 100),
                     labels = c('0%', '25%', '50%', '75%', '100%')) + 
  labs(# title = 'Species maps by taxonomic class',
       x = 'Class', 
       y = 'Percent of mapped species',
       fill = 'Dataset')
print(bar_taxa2)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), 
       width = 17.8, height = 7, units = 'cm')

@@

@@

### Manage scales for color and size 
scatter_quadplot <- scatter_quadplot +
  scale_colour_manual(values = c('LC' = 'green4', 
                                 'NT' = 'greenyellow', 
                                 'VU' = 'yellow', 
                                 'EN' = 'orange', 
                                 'CR' = 'orangered2',
                                 'DD' = 'grey30')) + 
  scale_size_continuous(limits = c(0, 100),
                        breaks = c( 0,    25,    50,    75,    100), 
                        labels = c('0%', '25%', '50%', '75%', '100%')) + 
  scale_x_continuous(expand = c(0, 0), 
                     limits = c(0, 102),
                     breaks = c(seq(0, 100, 25)),
                     labels = c('0%', '25%', '50%', '75%', '100%')) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 102),
                     breaks = c(seq(0, 100, 25)),
                     labels = c('0%', '25%', '50%', '75%', '100%'))

@@

# print(barchart_spp_risk_quads)
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'si_barchart_spp_risk_quads.png'),
       width = 17.8, height = 5, units = 'cm')

```
![](../figures/si_barchart_spp_risk_quads.png)

>>>>

# knitr::kable(taxa_df %>%
#                dplyr::select(class, 
#                              AquaMaps = n_am_class_all, 
#                              IUCN = n_iucn_class_all, 
#                              Both = n_class_both))
```

@@

bar_taxa2 <- ggplot(taxa_df_long2, aes(x = class, y = percent, fill = dataset)) +
  ggtheme_plot + 
  theme(panel.grid.major.x = element_blank()) +
  geom_bar(stat = 'identity', alpha = .8) +
#  scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
  scale_fill_manual(values = c('AquaMaps' = '#1b9e77', 'Both' = '#d95f02', 'IUCN' = '#7570b3')) +
  geom_text(aes(label = sprintf('n = %s', n_total), y = 102), 
            size = 2, 
            angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 130),
                     breaks = c(0, 25, 50, 75, 100),
                     labels = c('0%', '25%', '50%', '75%', '100%')) + 
  labs(# title = 'Species maps by taxonomic class',
       x = 'Class', 
       y = 'Percent of mapped species',
       fill = 'Dataset')

# print(bar_taxa2)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), 
       width = 17.8, height = 7, units = 'cm')

@@

![](../figures/bar_by_taxa_all.png)

@@

### Manage scales for color and size 
scatter_quadplot <- scatter_quadplot +
  scale_colour_manual(values = c('LC' = 'green4', 
                                 'NT' = 'greenyellow', 
                                 'VU' = 'yellow', 
                                 'EN' = 'orange', 
                                 'CR' = 'orangered2',
                                 'DD' = 'grey30')) + 
  scale_size_continuous(limits = c(0, 100),
                        breaks = c( 0,    25,    50,    75,    100), 
                        labels = c('0%', '25%', '50%', '75%', '100%')) + 
  scale_x_continuous(expand = c(0, 0), 
                     limits = c(0, 102),
                     breaks = c(seq(0, 100, 25)),
                     labels = c('0%', '25%', '50%', '75%', '100%')) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 103),
                     breaks = c(seq(0, 100, 25)),
                     labels = c('0%', '25%', '50%', '75%', '100%'))

@@

# print(barchart_spp_risk_quads)
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'si_barchart_spp_risk_quads.png'),
       width = 17.8, height = 4.5, units = 'cm')

![](../figures/si_barchart_spp_risk_quads.png)

### 2016-03-22 data_explore/data_explore_am_thresh.Rmd
All figures done? slap 'em together in Photoshop now.

hist_area_vs_threshold <- ggplot(spp_df3, aes(prop, fill = iucn_code)) + 
  ggtheme_plot + 
  geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 0.05, alpha = .7) + 
  geom_vline(xintercept = spp_df3_mean, color = 'darkred', linetype = 'dashed') + 
  annotate('text', x = spp_df3_mean, y = .13, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'mean') + 
  geom_vline(xintercept = spp_df3_med, color = 'grey30', linetype = 'dashed') + 
  annotate('text', x = spp_df3_med, y = .13, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'median') + 
  scale_fill_manual(values = c('LC' = 'green4', 
                               'NT' = 'greenyellow', 
                               'VU' = 'orange', 
                               'EN' = 'orangered2', 
                               'CR' = 'red4',
                               'DD' = 'grey60',
                               'NE' = 'grey70')) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = 'Proportion of range included when selecting a threshold of 0.4', 
       y = sprintf('Proportion of all aquamaps species (n = %s)', nrow(spp_df3)),
       fill = 'IUCN code')

@@

hist_area_vs_threshold2 <- ggplot(spp_df3a, aes(prop, fill = iucn_code)) + 
  ggtheme_plot + 
  geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 0.05, alpha = .7) + 
  geom_vline(xintercept = spp_df3a_mean, color = 'darkred', linetype = 'dashed') + 
  annotate('text', x = spp_df3a_mean, y = .16, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'mean') + 
  geom_vline(xintercept = spp_df3a_med, color = 'grey30', linetype = 'dashed') + 
  annotate('text', x = spp_df3a_med, y = .16, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'median') + 
  scale_fill_manual(values = c('LC' = 'green4', 
                               'NT' = 'greenyellow', 
                               'VU' = 'orange', 
                               'EN' = 'orangered2', 
                               'CR' = 'red4',
                               'DD' = 'grey60',
                               'NE' = 'grey70')) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = 'Proportion of range included when selecting a threshold of 0.4', 
       y = sprintf('Proportion of all aquamaps species (n = %s)', nrow(spp_df3a)),
       fill = 'IUCN code')

@@

  geom_ribbon(aes(ymax = quant95, ymin = quant05), alpha = .5, color = NA, fill = 'grey80') +
  geom_ribbon(aes(ymax = quant75, ymin = quant25), alpha = .5, color = NA, fill = 'grey70') +
  geom_line(color = 'grey30') + 
  # geom_line(aes(y = mean_prop), color = 'darkgreen') + 
  # geom_abline(intercept = area_mean_model[['coefficients']][1],
  #             slope     = area_mean_model[['coefficients']][2],
  #             color = 'red') + 
  geom_vline(xintercept = 0.40, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.50, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.60, color = 'blue', linetype = 'dashed') +
  annotate('text', x = .40, y = .05, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Halpern et al. 2012') + 
  annotate('text', x = .50, y = .05, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Klein et al. 2015') + 
  annotate('text', x = .60, y = .05, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Kaschner et al. 2006') + 
  # annotate('text', x = .75, y = .85,
  #          #size = 3, 
  #          color = 'grey20',
  #          label = 'R^2^ = .995') + 
  scale_x_continuous(expand = c(0, 0), 
                     breaks = c(  .2,    .4,    .5,    .6,    .8,   1.0),
                     labels = c('20%', '40%', '50%', '60%', '80%', '100%')
                     limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(# title = 'Relative species range after presence threshold',
       x = 'AquaMaps presence threshold cutoff', 
       y = 'Relative species range')

@@

ggsave(file.path(dir_fig, 'ribbon_am_threshold.png'), 
       width = 17.8, height = 6, units = 'cm')

>>>>

hist_area_vs_threshold <- ggplot(spp_df3, aes(prop, fill = iucn_code)) + 
  ggtheme_plot + 
  geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 0.05, alpha = .7) + 
  geom_vline(xintercept = spp_df3_mean, color = 'darkred', linetype = 'dashed') + 
  annotate('text', x = spp_df3_mean, y = .13, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'mean') + 
  geom_vline(xintercept = spp_df3_med, color = 'grey30', linetype = 'dashed') + 
  annotate('text', x = spp_df3_med, y = .13, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'median') + 
  scale_fill_manual(values = c('LC' = 'green4', 
                               'NT' = 'greenyellow', 
                               'VU' = 'orange', 
                               'EN' = 'orangered2', 
                               'CR' = 'red4',
                               'DD' = 'grey60',
                               'NE' = 'grey70')) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = 'Proportion of range included when selecting a threshold of 40%', 
       y = sprintf('Proportion of all aquamaps species (n = %s)', nrow(spp_df3)),
       fill = 'IUCN code')

@@

hist_area_vs_threshold2 <- ggplot(spp_df3a, aes(prop, fill = iucn_code)) + 
  ggtheme_plot + 
  geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 0.05, alpha = .7) + 
  geom_vline(xintercept = spp_df3a_mean, color = 'darkred', linetype = 'dashed') + 
  annotate('text', x = spp_df3a_mean, y = .16, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'mean') + 
  geom_vline(xintercept = spp_df3a_med, color = 'grey30', linetype = 'dashed') + 
  annotate('text', x = spp_df3a_med, y = .16, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'median') + 
  scale_fill_manual(values = c('LC' = 'green4', 
                               'NT' = 'greenyellow', 
                               'VU' = 'orange', 
                               'EN' = 'orangered2', 
                               'CR' = 'red4',
                               'DD' = 'grey60',
                               'NE' = 'grey70')) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = 'Proportion of range included when selecting a threshold of 40%', 
       y = sprintf('Proportion of all aquamaps species (n = %s)', nrow(spp_df3a)),
       fill = 'IUCN code')

@@

  geom_ribbon(aes(ymax = quant95, ymin = quant05), alpha = .5, color = NA, fill = 'grey80') +
  geom_ribbon(aes(ymax = quant75, ymin = quant25), alpha = .5, color = NA, fill = 'grey70') +
  geom_line(color = 'grey30') + 
  # geom_line(aes(y = mean_prop), color = 'darkgreen') + 
  # geom_abline(intercept = area_mean_model[['coefficients']][1],
  #             slope     = area_mean_model[['coefficients']][2],
  #             color = 'red') + 
  geom_vline(xintercept = 0.40, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.50, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.60, color = 'blue', linetype = 'dashed') +
  annotate('text', x = .39, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Halpern et al. 2012') + 
  annotate('text', x = .49, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Klein et al. 2015') + 
  annotate('text', x = .59, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Kaschner et al. 2006') + 
  # annotate('text', x = .75, y = .85,
  #          #size = 3, 
  #          color = 'grey20',
  #          label = 'R^2^ = .995') + 
  scale_x_continuous(expand = c(0, 0), 
                     breaks = c(  .2,    .4,    .5,    .6,    .8,   1.0),
                     labels = c('20%', '40%', '50%', '60%', '80%', '100%'),
                     limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1.01)) +
  labs(# title = 'Relative species range after presence threshold',
       x = 'AquaMaps presence threshold cutoff', 
       y = 'Relative species range')

@@

ggsave(file.path(dir_fig, 'ribbon_am_threshold.png'), 
       width = 17.8, height = 7, units = 'cm')
